\documentclass[10pt]{article}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{url}

\begin{document}
\title{EE106A: Zumy Troubleshooting Guide}
\author{Victor Shia, Jaime Fisac}
\date{October 1, 2015}
\maketitle

\emph{Relevant Tutorials and Documentation:} 
\begin{itemize}
\item \verb=odroid_machine=: \url{https://github.com/vshia/odroid_machine}
\item \verb=zumy_teleop=: \url{https://github.com/jlamyi/zumy_teleop}
\item \verb=man_joy_override=: \url{https://github.com/jlamyi/man_joy_override}
\end{itemize}

\tableofcontents


\section{Troubleshooting the Zumy}
As the Zumys are new research devices, there will be times that you run into trouble with the Zumys.
This guide has been divided into different sections: connecting and running.
For this guide, we will assume the Zumy's name is zumy6.  
For your own zumy, change zumy6 to zumy\# as appropriate.

\section{Issues with Connecting to the Zumy} \label{connecting}

\begin{enumerate}
  \item Can you ping the zumy?  (\verb=ping zumy6.local=) \label{ping}
  \begin{enumerate}
    \item No - is the computer connected to the wifi network: ZumyRouter 
    \item No - try reconnecting to the network: ZumyRouter
    \item No - try restarting the computer (sometimes this helps with the wifi connection)
    \item Yes - move on. 
  \end{enumerate}
  \item Can you SSH into the Zumy?  (\verb=ssh zumy@zumy6.local=)
  \begin{enumerate}
    \item No - Go back to Subsection \ref{ping}
    \item Yes - Do you need to type in the password?  If yes, redo your SSH keys.  If no, move on.
  \end{enumerate}
  
\end{enumerate}

\section{Issues with the Zumy suddenly not responding after starting roslaunch}
\begin{enumerate}
  \item Can you ping it?  (If not, goto Section \ref{connecting})
  \item Is the Zumy still on? (sometimes it turns off)
  \begin{enumerate}
    \item No - turn it on and try again
    \item Yes - move on. 
  \end{enumerate}  
  \item Is the Zumy tethered to the power supply?
  \begin{enumerate}
    \item Yes - Is the power supply at 12V?
    \item Yes - Try a fresh battery
    \item No - Move on
  \end{enumerate}  
  \item Is the Zumy using a battery?
  \begin{enumerate}
    \item Yes - switch batteries
    \item No - use a fresh battery
  \end{enumerate}  
\end{enumerate}

One thing we've discovered with the Zumy is that when it is tethered, it tends to draw more power than the power supply can give.
When that happens, the Zumy suddenly stops responding.
This issue does \textbf{not} occur with the battery.
Our suggestion is to tether the Zumy to the power supply when you are just getting started (setting up the Zumy, SSH keys, etc)
When you actually want to run the lab and have the Zumy move, use the battery.

\section{Issues with Driving the Zumy around}

\begin{enumerate}
  \item Can you ping it?  (If not, goto Section \ref{connecting})
  \item Restart the Zumy
  \item Look at the rqt\_graph to make sure your nodes and topics are correct
\end{enumerate}

\end{document}
